---
title: "Assignment1"
author: "MA_615"
date: "9/23/2021"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
#load the data
library(tidyverse)

# call built-in data mtcars.
data(mtcars)

# Select only car models where mpg<20
mtcars_mpg2 <- mtcars[mtcars$mpg < 20,]


# Reduce the variables to mpg, cyl, disp, hp, gears
mtcars_mpg2 <- mtcars_mpg2[, c(1,2,3,4,10)]

```
I learned how read the data that I need from a big dataset, and reduce variables to create a new dataset which is more simple and easy to read.

```{r}
# read the R file hand_functions.R so that it can be used
# notice that with echo = TRUE 
source(file = "hand_functions.R", echo = TRUE)

# Now use the function from hand_functions.R

sp_out <- sum_special(mtcars_mpg2)

#using the function to calculate the summary statistics of the data frame
```
I learned that we can use formula that was save in a file to do computation which will save a lot of time. And that also means that we do not need to do a long calculation in our rmd file to find a function that fit into our analysis, which make our rmd more concise. In addition, if we need to use a formula repeatedly, a function file that is ready to use will be really helpful.
```{r}

library(esquisse)

#esquisser(data = mtcars_mpg2, viewer = "browser")


# graph the ggplot in esquisse as same as needed
#then copy the code from esquisse and insert to my script here.

ggplot(mtcars_mpg2) +
  aes(x = disp, y = mpg) +
  geom_point(shape = "bullet", size = 4L, colour = "#B22222") +
  geom_smooth(span = 0.5) +
  theme_minimal()
```
I learned how to use esquisse to make simple plots using esquisse and apply different features or limitation to the plots.

```{r}
# note that this boxplot cannot be made with esquisse() unless
# the data is adjusted.  What adjustment is needed?

#adjust cyl as a factor so that esquisse can read it 
cyl_adjusted<- as.factor(mtcars_mpg2$cyl)

#group two data frames with same number of rows into a single data frame
mtcars_mpg2 <-cbind(mtcars_mpg2, cyl_adjusted)

#draw the plot in esquisse
#esquisser(data = mtcars_mpg2, viewer = "browser")


ggplot(mtcars_mpg2) +
 aes(x = cyl_adjusted, y = mpg) +
 geom_boxplot(shape = "circle", fill = "#625ACD", alpha=0.2) +
 theme_minimal()



```
I learned how to adjust my data frame when esquisse can read my data frame as a factor. And also learned how to combine two data frames with same length of rows into a single data frame.

